\chapter{Conclusion}\label{ch5}

We have successfully implemented the complete, reliable and coherent system for more efficient face fitting pipeline. We have taken a modularized approach to tackle this problem. By separating data acquisition (including the module which handles all the camera related processes), shape fitting and color fitting modules from each other, we have made the system useful for any future application that will either make use of one of the modules or all of them together. We have introduced an alternative, more efficient way of a standard 3DMM face fitting by relying on a point cloud information obtained from the consumer depth camera. We have shown that our method produces especially good shape reconstructions in comparison to previous approaches. This was achieved by fitting the 3D Morphable model to the point cloud first to obtain an accurate shape and pose parameters. Those parameter sets are very important prerequisites for the color fitting module and directly influence the final reconstructions. The parameter set that is produced by the shape fitting module, is getting utilized by the color fitting module to obtain final face reconstruction. Based on more accurate shape reconstruction, our method also attempts to capture more specific details of the target face in the image. \bigskip

We have presented an evaluation of our proposed shape and color fitting modules, as well as, comparison of our final results and the previous approaches. Our final reconstructions are noticeably better than previous methods. Especially stands out the shape reconstruction quality, which we measure based on average mesh distances. This was expected since, out method has an actual shape information to rely on during the fitting process. When comparing our shape and color fitting modules we have observed a slight decrease in the shape quality. This is because of the color fitting module requiring additional adjustments throughout the process to correctly infer the color information from the image. The decrease in shape quality also is due to increased difficulty of the fitting problem during the color fitting phase. Despite this decrease, final reconstructions that our method produces are still more accurate than previous method results. Our method performs noticeably better in full-frontal shots and suffers mainly when yaw rotation is introduced. This is due to the landmark detection algorithm onto the image, which provides all landmarks whether the landmark point is visible or not. This is not necessarily optimal for our application because pixels that get de-projected incorrectly might cause problems for shape fitting.\bigskip

We have also presented a demo implementation of our shape fitting module into the already existing Scalismo Face Morpher web service. 
Since our system is module based, this kind of implementations are straightforward and can be easily preformed for any future applications. 





